Are people really struggling to find a job?

### 2024-03-23 paper/paper.qmd
updated paper

- `Youth Unemployment` is the dependent variable we are trying to predict. These are generally categorized as people who are between the ages of 15-24.
- `Education Level` is an independent variable representing the level of education. (e.g., high school, undergraduate, postgraduate) 
- `Reference Period` is another independent variable that represents the time frame of the data collection (e.g., year).
- `Adult Unemployment` and `Senior Unemployment` are independent variables representing unemployment rates for adult and senior age groups, with people ages ranging between 25-44 and above 45, respectively.
- `$\beta_0$` is the y-intercept, representing the expected value of `Youth Unemployment` when all the independent variables are 0.
- `$\beta_1, \beta_2, \beta_3, \beta_4$` are the coefficients for each independent variable, representing the change in `Youth Unemployment` for a one-unit change in the respective independent variable, holding all other variables constant.
- `$\epsilon$` represents the error term, accounting for the variability in `Youth Unemployment` not explained by the model.

@@

## First discussion point {#sec-first-point}

>>>>

- `Youth Unemployment` is the dependent variable we are trying to predict. These are generally categorized as people who are between the ages of 15-24.
- `Education Level` is an independent variable representing the level of education. (e.g., high school, undergraduate, postgraduate) 
- `Reference Period` is another independent variable that represents the time frame of the data collection (e.g., year).
- `Adult Unemployment` and `Senior Unemployment` are independent variables representing unemployment rates for adult and senior age groups, with people ages ranging between 25-44 and above 45, respectively.
- $\beta_0$ is the y-intercept, representing the expected value of `Youth Unemployment` when all the independent variables are 0.
- $\beta_1, \beta_2, \beta_3, \beta_4$ are the coefficients for each independent variable, representing the change in `Youth Unemployment` for a one-unit change in the respective independent variable, holding all other variables constant.
- $\epsilon$ represents the error term, accounting for the variability in `Youth Unemployment` not explained by the model.

@@

## First discussion point
